\thesistitle

### 2019-07-23 sections/background.tex
Xander discussion

\section{Clone Types} \label{chap:backgroundclonetypes}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and refactor. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

@@

\section{Code clone harmfulness}
Although duplication in source code is generally seen as a harmful coding practise that should be avoided. Most papers view clones as harmful regarding program maintainability. \textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well. Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work''} \cite{ostberg2014automatically}. However, in some instances it is undesirable to remove all duplication, as it can lead to unnecessary complexity.

@@

Regarding refactoring, a software system can often not change the source code of its dependencies. This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system. Because of that, in this study, we consider external classes to see what impact they have on the refactoring process.

>>>>

\section{Clone Types} \label{chap:backgroundclonetypes}
\simon{What is Structurally/syntactically/functionally/textually, ect ect, all words before EQUAL}
Duplication in code is found in many different forms. Most often duplicated code is the result of a programmer reusing previously written code \cite{haefliger2008code, baxter1998clone}. Sometimes this code is then adapted to fit the new context. To reason about these modifications, several clone types have been proposed. These clone types are described in Roy et al \cite{roy2007survey}:
\begin{displayquote}
\textbf{Type I:} Identical code fragments except for variations in whitespace (may be also variations in layout) and comments.\\
\textbf{Type II:} Structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments.\\
\textbf{Type III:} Copied fragments with further modifications. Statements can be changed, added or removed in addition to variations in identifiers, literals, types, layout and comments.\\
\textbf{Type IV:} Two or more code fragments that perform the same computation but implemented through different syntactic variants.
\end{displayquote}
A higher type of clone means that it's harder to detect and refactor. There are many studies that adopt these clone types, analyzing them further and writing detection techniques for them \cite{sajnani2016sourcerercc, kodhai2010detection, van2019novel}.

@@

\section{Code clone harmfulness}
\simon{You make a promise here. Do we need this section? Maybe remove it completely.}
Although duplication in source code is generally seen as a harmful coding practise that should be avoided. Most papers view clones as harmful regarding program maintainability. \textit{``Clones are problematic for the maintainability of a program, because if the clone is altered at one location to correct an erroneous behaviour, you cannot be sure that this correction is applied to all the cloned code as well. Additionally, the code base size increases unnecessarily and so increases the amount of code to be handled when conducting maintenance work''} \cite{ostberg2014automatically}. However, in some instances it is undesirable to remove all duplication, as it can lead to unnecessary complexity.

@@

Regarding refactoring, a software system can often not change the source code of its dependencies. This can sometimes be a burden, when an external dependency does not use proper abstractions that are required by a software system. Because of that, in this study, we consider external classes to see what impact they have on the refactoring process.
\simon{Adapter pattern?}

### 2019-07-23 sections/research.tex
Xander discussion

\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature. These simple definitions are suitable for analysis of a codebase. Their detection results in simple to understand numbers to argue about a codebase. However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code are functionally related. For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.

@@

\section{Shortcomings of clone types}
Clone type 1-3 (further explain in section \ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system. Clones by these definitions can relatively easily and efficiently be detected. This has allowed for large scale analyses of duplication~\cite{livieri2007very}. However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.

@@

Type 1 clones are by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating} implemented as textual equality between code fragments (except for whitespace and comments). Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases, refactoring opportunities could be invalidated. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone. When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type2}
  \caption{Variables with different types but the same name.}
  \label{fig:type2variables}
\end{figure}

@@

We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored. Type 1R clones are a subset of type 2R clones. All rules that apply to type 1R clones also apply to type 2R clones. Additionally, type 2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold. Type 2R do not allow any variability in types, as opposed to type 2 clones which do allow variability in types. As type 2R clones are per definition more permissive than type 1R clones, type 1R clones are a subset of type 2R clones.

\subsubsection{A threshold for variability in literals, variables and method calls}\label{sec:variabilitythreshold}
Type 2 clones allow any variability in literals, variables and method identifiers. However, this information tells a lot about the meaning of the code fragment. Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many. However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.

@@

\begin{eqfloat}\label{eq:type2r}
$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
$$Total = \text{Total number in the clone instance}$$
$$l = \text{Literals in clone}$$
$$v = \text{Variables in clone}$$
$$m = \text{Method calls in clone}$$
$$t = \text{Tokens in clones}$$
\caption{Type 2R variability threshold formula}\end{eqfloat}

>>>>

\chapter{Defining refactoring-oriented clone types}\label{chap:clonetypes}
In section \ref{chap:backgroundclonetypes} we introduced the four clone types as defined in literature. These simple definitions are suitable for analysis of a codebase. Their detection results in simple to understand numbers to argue about a codebase. However, these clone types have a few flaws which makes it hard to argue to what extend two fragments of code can and should be refactored. For each of type 1-3 clones~\cite{roy2007survey} we list our solutions to their shortcomings to increase the chance that we can refactor the clone while improving the design.

@@

\section{Shortcomings of clone types}
Clone types 1-3 (further explained in section \ref{chap:backgroundclonetypes}) allow reasoning about the duplication in a software system. Clones by these definitions can relatively easily and efficiently be detected. This has allowed for large scale analyses of duplication~\cite{livieri2007very}. However, these clone type definitions have shortcomings which makes the clones detected in correspondence with these definitions less valuable for (automated) refactoring purposes.

@@

Type 1 clones are implemented as textual equality between code fragments (except for whitespace and comments) by most clone detection tools~\cite{kamiya2002ccfinder, semura2017ccfindersw, roy2008nicad, svajlenko2016bigcloneeval, svajlenko2014evaluating}. Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases, refactoring opportunities could be invalidated. This can make type 1 clones less suitable for refactoring purposes, as they require additional judgment regarding the refactorability of such a clone. When aiming to automatically refactor clones, applying refactorings to type 1 clones is bound to be error prone and can result in an uncompilable project or a difference in functionality.

@@

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/type2}
  \caption{Variables with different types but the same name.}
  \label{fig:type2variables}
\end{figure}
\todo{image is not correct}

@@

We tackle these problems with type 2R clones to be able to detect such clones that can and should be refactored. Type 1R clones are a subset of type 2R clones \todo{Define this subset relation}. All rules that apply to type 1R clones also apply to type 2R clones\todo{Rules....}. Additionally, type 2R clones allow variability in literals, variables and method calls. This variability however is constrained by a threshold, which is explained in more detail in section \ref{sec:variabilitythreshold}.%to limit the negative effect on system design of variability in these expressions after refactoring.

\subsubsection{A threshold for variability in literals, variables and method calls}\label{sec:variabilitythreshold}
\simon{Check this text... Harmfulness?! ???}
Type 2 clones allow any variability in literals, variables and method identifiers. However, this information tells a lot about the meaning of the code fragment. Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many. However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.

@@

\simon{Dividing expressions by tokens... maybe not do that. How to do it then??????}
\begin{eqfloat}\label{eq:type2r}
$$\text{T2R Variability Percentage}=\frac{Diff(l) + Diff(v) + Diff(m)}{Total(t)}*100$$
$$Diff = \text{Amount that differ from other clone instances in the clone class}$$
$$Total = \text{Total number in the clone instance}$$
$$l = \text{Literals in clone}$$
$$v = \text{Variables in clone}$$
$$m = \text{Method calls in clone}$$
$$t = \text{Tokens in clones}$$
\caption{Type 2R variability threshold formula}\end{eqfloat}
